---
title: "My First file for Git"
author: "Lo Thi Duc"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: true
    code_folding: hide

---
# Data analysis that will be automated
We provide here some basic elements about the data set and descriptive statistics on some variables of interest.  

* First we load the data
* second we print a summary


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(magrittr) 
library(dplyr)
library(flextable)
library(ggplot2)
setwd("C:/Users/ltduc.TCTK/OneDrive/diske/coursera/SIAP/Automated Reports")
TradeData <- read.csv("Data/TradeData.csv")
head(TradeData)
```

We loaded the data set and compile the  report on `r Sys.Date()`

## Summary statistics
Here are some summary statistics of the export value (*Stat_Value* variable), all products combined:

```{r }
summary(TradeData$Stat_Value)
```

The data set contains   **`r  nrow(TradeData)`  observations**, and  **`r  ncol(TradeData)`** variables.

Here is a list of all variables available in the data set: 

```{r}
names(TradeData)
```

## Type of exports

The variable *Principle_Export* list all the types of goods exported from Vanuatu. There are **`r length(unique(TradeData$Principle_Exports))`** different goods exported. Let's have the list of all these goods. 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
unique(TradeData$Principle_Exports)

```
## Analysis of Vanuatu's exports
### Principle exports statistics

The table below show all principle exports and their total values in USD: 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(dplyr) 
library(tidyverse)
library(flextable)
ExportsByType <- TradeData %>%
 group_by(Principle_Exports) %>%
 summarise(total = sum(Stat_Value)) %>%
 arrange(desc(total))

flextable(ExportsByType)
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
max_row <- ExportsByType[which.max(ExportsByType$total), ]
min_row <- ExportsByType[which.min(ExportsByType$total), ]
```


**`r max_row$Principle_Exports`** has been exported in the highest value of all principle exports; it is **USD `r max_row$total`**, whereas **`r min_row$Principle_Exports`** is the smallest; at only **USD `r min_row$total`**

### Identity of Exports from Vanuatu, 2000-2010

The graph depicts the volume of all export products in the 2000-2010 period.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
ExportsByType %>%
 ggplot()+
 aes(x = Principle_Exports, y = total) +
 geom_bar(stat = "identity") + 
 labs(title ="Exports from Vanuatu [ 2000-2010] ", 
      subtitle = "National Statistical Office",
      caption = paste("Date: ",Sys.Date()),
      x= "Exports categories",
      y = "Vatu") +
 coord_flip()

```

